How to compute the fusion product of MV cycles in type A

### 2021-04-16 draft.tex
Fixed a typo.

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ \acom{definiton, no boldface}
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ 
% such that $ L $ 
which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

@@

\begin{enumerate}
    % TODO: I think it makes more sense to put the first point at the end; it just relates (fibres of) the BD Gr to the ordinary Gr
    % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
    \item 
    %We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
    % $$ \Grbd \rightarrow \Grth $$ 
    We define a map $ \Grbd \rightarrow \Grth $ by \acom{Don't we also want to restrict $V$}
    $$
    (V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})\,.
    $$
    % 
    % It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
    In group-theoretic terms, on the fibre over $ s $, this is the inclusion
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}
    % 
    Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
    \begin{equation*}
    % \label{eq:grbdgrs}
    \Gr_{0,s} \cong 
    \begin{cases} 
        \Gr \times \Gr_s & s \ne 0 \\
        \Gr              & s = 0\,.
    \end{cases}
    \end{equation*}
    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.

@@

Let $ \Gr_{0, \CC^\times} $ denote the preimage of $ \Gr_{0, \AA} $ under the map $\Gr_{0,\AA} \rightarrow \AA $.  Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above) we obtain
$$
\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr_{\CC^\times} \rightarrow \Gr \times \Gr
$$
where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.  (This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
\jcom{I added the def of $ \Gr_{0, \CC^\times}$ but not $ \Gr_{\CC^\times}$.  We could drop it and condense the definition of $ \tau$ to one map.}

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
\begin{equation*}
    % \label{deservesdisplay}
    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
\end{equation*}
which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% 
By construction, 
% \acom{technically, there were two given above, so *these* constructions?} 
$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$. \acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.  I just taught this on the last day of my algebraic geometry class!}

@@

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes}

@@

\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
\jcom{I fixed it now.  I didn't want to use ES's $a_i$.}

@@

\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.  I changed the wording of ``reproduce''. I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}

@@

\subsection{The Mirkovic--Vybornov slice} 
% 
Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
\begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
\end{definition}
\jcom{I'm not a huge fan of this description, but I don't know how to write it better.}

\acom{Agree. Happy to just have the in-words description.}

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 

@@

\section{Exposition}

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda'), (s,\lambda'')$.
        \item $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
        % \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

@@

    \rcom{Preimage of $\beta_\mu$}

@@

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t]) $.  Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $. % \CC\xt[t^{-1}]s

    \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}

    \acom{Si}

    Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
    \end{proof}

@@

\section{Falling Action} % Resolution
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}

\section{Denouement}
\label{s:denouement}
% 
In this section we demonstrate how to put the main results of this paper into practice.
% 
Given $\lambda$ dominant effective and $\mu\le\lambda$ effective, let $YT(\lambda)_\mu$ denote the set of semistandard Young tableaux of shape $\lambda$ and weight $\mu$. 
%

We need the following result from \cite{dthesis}.
\begin{proposition}
    Generalized orbital varieties are indexed by semistandard Young tableaux. Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
    \[
        YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
    \]
    % $$
    % \begin{tikzcd}
    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
    % \end{tikzcd}
    % $$
\end{proposition}
% 
Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. 
% 
\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        \label{eq:tabmult}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z(\tau), Z'\circ Z''
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z(\tau)]
    \end{equation}
    and the intersection multiplicities on the right are found by the algorithm described in \Cref{ss:algo}.

    \acom{Add pseudocode}

>>>>

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. 
% \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
By restriction $ K^m$ can be viewed as an $R$-module.  An \textbf{$R$-lattice} in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ 
% such that $ L $ 
which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

@@

\begin{enumerate}
    % TODO: I think it makes more sense to put the first point at the end; it just relates (fibres of) the BD Gr to the ordinary Gr
    % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
    \item 
    %We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
    % $$ \Grbd \rightarrow \Grth $$ 
    We define a map $ \Grbd \rightarrow \Grth $ by 
    % \acom{Don't we also want to restrict $V$} 
    % Joel says nope, restriction of vector bundle corresponds to specialization of lattice; here the map is inclusion  
    $$
    (V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})\,.
    $$
    % 
    % It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
    In group-theoretic terms, on the fibre over $ s $, this is the inclusion
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}
    % 
    Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
    \begin{equation*}
    % \label{eq:grbdgrs}
    \Gr_{0,s} \cong 
    \begin{cases} 
        \Gr \times \Gr_s & s \ne 0 \\
        \Gr              & s = 0\,.
    \end{cases}
    \end{equation*}
    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.

@@

Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above) we obtain
$$
\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr_{\CC^\times} \rightarrow \Gr \times \Gr
$$
where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.  (This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
\jcom{I added the def of $ \Gr_{0, \CC^\times}$ but not $ \Gr_{\CC^\times}$.  We could drop it and condense the definition of $ \tau$ to one map.}
\acom{Todo --- We resolved to rewrite $\tau$ as gluing of the composition above restricted to fibres}

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
\begin{equation*}
    % \label{deservesdisplay}
    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
\end{equation*}
which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% 
By construction, 
% \acom{technically, there were two given above, so *these* constructions?} 
$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$. \acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.  I just taught this on the last day of my algebraic geometry class!} \acom{Cool! That Proposition is a bit more general too..}

@@

Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$? Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}

@@

\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}

Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
$$
    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
$$
\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
\acom{\emoji{+1}}

@@

\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.  I changed the wording of ``reproduce''. I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
\acom{\emoji{+1}}

@@

\subsection{The Mirkovic--Vybornov slice} 
% Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
% \acom{I don't suppose we need this basis now that we're just describing $\TT_\mu$ in words.}
% \begin{definition}
An element of the \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ 
% defined as the set of $A\in M_N(\CC)$ such that 
    %     \begin{aligned}
    %         &\text{for all } 1 \le a,s\le m\,,
    %         \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
    %         &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
    %         &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
    %     \end{aligned}    
% \end{definition}
% \jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
% \acom{Agree. Happy to just have the in-words description.}
    % In words, $A$ 
    is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 

@@

\section{Exposition}
\label{s:exposition}

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $((0,\lambda'), (s,\lambda''))$.
        \item $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
        % \acom{why no $G(\CC[t])$-coset?}
    \end{enumerate}
\end{lemma}

@@

    \rcom{Preimage of $\beta_\mu$}  
    % 
    \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}

@@

\begin{proof}
    Let $ L $ 
    % lie in this image.  
    be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$. Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N_-(\cK_\infty)$ and so we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.

    Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $. % \CC\xt[t^{-1}]s
% 
% \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?} % 
% \acom{Si.}
% 
    Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
    \end{proof}

@@

\section{Falling Action} % Resolution
\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}

\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}
% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
In this part we prove that 
% the ideal of 
$Z'\ast_\AA Z''$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$.
% 
Given $\lambda$ dominant effective and $\mu\le\lambda$ effective, let $YT(\lambda)_\mu$ denote the set of semistandard Young tableaux of shape $\lambda$ and weight $\mu$. 
%

We need the following result from \cite{dthesis}.
\begin{proposition}
    % Generalized orbital varieties are indexed by semistandard Young tableaux. 
    There are bijections 
    % Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
    \[
        YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
    \]
    Moreover, there is a \acom{partial?} inverse 
    \[
    \CC[N]\to \bigcup_{\lambda~\text{dominant}\atop \mu\le\lambda} YT(\lambda)_\mu \,. 
    \]
    % $$
    % \begin{tikzcd}
    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
    % \end{tikzcd}
    % $$
\end{proposition}
% 
\acom{Refer to Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
\jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}

Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?}

% 
% 
% TODO: Not yet, that would be the algo stuff that we are holding off on 
% In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
% 
% In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles. 
% 
% and recall the $\mu$-numeration of the standard basis of $\CC^N$. 
% TODO: can't we do without it^^
Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors. Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes. If the tableau contains repeated entries then first means leftmost.
